\chapter{Conclusion}

In this thesis,
we have investigated the design of practical threshold key generation and signing schemes.
We have presented several constructions that minimize barriers to implementation,
including reducing network latency and communication overhead,
and limiting state-keeping.

In Chapter~\ref{chp:frost},
we presented FROST,
a Flexible Round-Optimized Schnorr Threshold Signature.
We showed how FROST can be used either as a two-round protocol,
or optimized to a single-round online signing protocol with a batched preprocessing phase.
As discussed in
Section~\ref{intro:impact},
FROST has already found use in practice,
and will likely become the scheme of choice in the future for thresholdizing Schnorr signatures in practical applications.

In Chapter~\ref{chp:storm},
we presented new game-based definitions for distributed key generation schemes.
We then presented a generic construction that employs as building blocks a non-interactive key-exchange (NIKE) scheme,
an aggregated verifiable secret sharing (AgVSS) scheme,
and a secure hash function.
We then presented Storm,
a concrete instantiation of our generic construction that is secure assuming the hardness of the Computational Diffie-Hellman (CDH) assumption.

Finally, in Chapter~\ref{chp:arctic},
we presented Arctic,
a deterministic and stateless threshold Schnorr signature scheme.
Arctic builds upon pseudorandom secret sharing as a building block,
and allows all participants to perform a two-round threshold signing operation,
without requiring participants to maintain state in between or across signing
rounds.
Arctic requires the assumption of an honest majority,
and is efficient for small signing groups (i.e., when the total number of
possible signers is less than $25$).

The thesis statement,
as given in Chapter~\ref{chp:intro},
is that it is possible to construct efficient threshold key generation and signature schemes that are practically useful.
The three constructions we present in this thesis are optimized for efficiency,
simplicity,
and low round complexity,
and are among the most efficient in the literature,
while maintaining backwards compatibility with existing centralized schemes,
often a key priority in practice.
The real-world deployment of FROST in particular underscores that this thesis statement is true.

\section{Future Work}

While this thesis presents advancements in the design of practical threshold key generation and signatures,
many problems remain.
For example, this thesis largely considers the problem of efficient and practical threshold Schnorr signatures.
However, it is possible that the techniques employed in this work are equally applicable in the setting of other signature schemes,
such as threshold ECDSA.
While randomized threshold ECDSA signatures under honest-majority assumptions exist that similarly build upon pseudorandom secret sharing~\cite{DamgardJNPO22,DoernerKLS23,DalskovOKSS20},
the techniques we employ in FROST may likewise potentially be applicable to improving the efficiency of threshold ECDSA signatures.

Another avenue for future research is the investigation of the minimal security
assumptions required for two-round threshold Schnorr signature schemes.
While Arctic can be proven under standard assumptions,
FROST requires the stronger Algebraic One-More Discrete Logarithm (AOMDL)
assumption.
It is interesting to consider whether this difference is inherent,
or if it is possible to prove two-round randomized Schnorr threshold signature
secure under weaker assumptions.

\section{Reflections}

While threshold signatures have been extensively studied in the literature for decades,
it is only more recently that threshold signatures have enjoyed adoption in practice.
With the increase in real-world deployments,
additional requirements have been introduced for the design of threshold signatures,
including simplicity,
minimizing round complexity,
and backwards compatibility with single-party signature schemes,
such as Schnorr signatures.
These new requirements in practice have led to the research presented in this thesis.

What does the future hold for threshold signatures and distributed key generation?
Clearly,
investigating how to define quantum-secure (and practical) versions of these schemes is an immediate priority.
However,
as threshold signatures gain more widespread adoption,
it will be interesting to see what additional practical requirements emerge.
In particular,
using threshold cryptography beyond the core current use case of securing cryptocurrencies is an important next step.
Hopefully,
threshold cryptography will continue to prove its relevance in the real world by distributing trust,
in a wider range of use cases in the future.



