% \addcontentsline{toc}{chapter}{Introduction}
% \begin{center}\textbf{Introduction}\end{center}
%======================================================================
\chapter{Introduction}
\label{chp:intro}
%======================================================================

While the goal of cryptography can be described in many ways,
one common motivation is often \emph{authorization} within a digital environment;
i.e., the assurance that only a designated party is allowed to perform some action.
The goal of authorization is generally accomplished by granting the authorized party \emph{knowledge} of a secret,
and then later challenging the party to demonstrate knowledge of this secret value.
This intuition describes the strategy underlying interactive identification
protocols and digital signature schemes--common cryptographic building blocks in secure protocols.

A challenge emerges when considering the possibility that this authorized party may later become compromised by an adversarial party,
or might simply fail.
For example,
a database holding a secret value might become corrupted.
One real-world example is that of certificate authorities,
which have been long-documented to perform untrusted actions~\cite{SSLMate}
In this setting,
even if the designated party correctly demonstrates knowledge of a secret key,
the party may still violate trust.

As cryptographers,
the question then emerges as whether new cryptographic primitives can be designed to better reflect the trust required in a real-world setting.
For this particular example,
instead of distributing one secret value to authorize a designated party,
one might ask whether is it possible to instead designate multiple parties that must cooperate to perform a trusted action.

In this dissertation,
we address this question by investigating the real-world utility of \emph{threshold} schemes.
Threshold schemes are a critical cryptographic primitive that
requires at least a threshold $t$ parties out of a set of $n$ total parties to collaborate to perform some function.
This function depends on the use case.
For example,
the parties might perform threshold signing~\cite{KomloG20,BellareCKMTZ22,Lindell22},
outputting a joint signature at the end of the protocol.
Alternatively, participants might participate to jointly generate cryptographic key
material~\cite{Pedersen91,GennaroJKR07,KomloG20,Groth21,GurkanJMMST21,BonehS2020,NejiBR16,Lindell22,DasYXMKR21,BachoL22,AbrahamJMMS2022}.
This key may then be used within the context of other threshold schemes,
such as evaluating a pseudorandom function (PRF) in a threshold manner~\cite{JareckiKR18}.

Threshold schemes are an appealing primitive due to their ability to ensure robustness in the case of failure,
and to distribute trust among many parties.
In particular,
the security of the scheme assumes $t-1$ players are corrupted,
and so can deviate arbitrarily from the protocol.
The security of the scheme ensures that in spite of a subset of corrupted players,
the scheme remains secure.
%
As such,
threshold schemes offer practical security benefits,
allowing for dynamic key management and defense in depth against potential adversarial corruptions.
While some threshold schemes can be instantiated by each party simply performing a single-party protocol in parallel,
a practical goal for many threshold schemes is to preserve compatibility with existing single-party schemes,
to minimize implementation complexity and to ensure efficiency.

\paragraph{Motivation.}
Interest in threshold schemes is growing in practice.
For example,
as of early 2025, NIST is expected to issue a call for threshold schemes ranging from distributed key
generation to threshold zero-knowledge proofs~\cite{NIST22,NIST23}.
The NIST call specifically requests threshold variants of single-party signature schemes,
including Schnorr signatures~\cite{Schnorr91},
which is a core focus of this thesis.
%Another example is the FROST Schnorr threshold signature scheme~\cite{KomloG20,BellareCKMTZ22},
%for which an IRTF RFC exists~\cite{Connolly22}.

However,
significant challenges arise when using threshold schemes in practice,
such as gracefully handling failure cases,
performing multi-party operations at scale,
and operating in a setting where signers are not guaranteed to always be online.
Furthermore,
multi-party, multi-round schemes such as threshold signatures introduce
significant complexity and performance costs over single-party signature
schemes.
For this reason,
schemes that are simple to implement, provide defense-in-depth measures, and incur low round complexity are attractive in practice.
However, such schemes are difficult to prove secure using standard security assumptions.
For example, for discrete logarithm-based threshold signatures,
the most efficient two-round schemes require the one-more discrete logarithm
assumption to demonstrate unforgeability~\cite{KomloG20,BellareCKMTZ22},
whereas less-efficient three-round schemes can be proven secure using the
discrete logarithm assumption directly~\cite{CritesKM23,BellareCKMTZ22,Lindell22}.

\paragraph{Problem to Overcome.}
While threshold schemes offer benefits such as redundancy and increasing the
cost to a potential adversary,
the downside to threshold schemes in practice is their complexity and
performance overhead.
Multi-round, multi-entity protocols incur additional performance and complexity challenges beyond the single-party setting.
These challenges are compounded when considering real-world failures,
such as network failures and timeouts.
As such, even though efficient threshold schemes might possibly incur stronger security assumptions,
these tradeoffs are often practically worthwhile when considering improvements in reduced complexity and increased performance.

With the goals of efficiency, simplicity, and security in mind,
in this work,
we investigate how to design efficient threshold schemes,
and propose a range of constructions that provide improved efficiency over
prior works in the literature.
In particular,
our thesis statement is as follows:


\begin{quote}
  \it
  \begin{sloppypar}
It is possible to construct efficient threshold key generation
and signature schemes that are practically useful,
with reasonable security assumptions.
By practical utility,
we refer to the properties that implementations often require,
such as the simplicity of the scheme,
low number of communication rounds among parties,
and computational and bandwidth efficiency.
  \end{sloppypar}
\end{quote}

\section{Overview of Results}

This dissertation presents new techniques to simplify and improve the practicality of threshold Schnorr signatures and discrete-logarithm based distributed key generation.
Chapter~\ref{chp:frost} gives an efficient randomized threshold Schnorr signature scheme,
Chapter~\ref{chp:storm} gives a generic construction for a distributed key generation (DKG) scheme.
Chapter~\ref{chp:arctic} gives an efficient deterministic threshold Schnorr signature scheme.

\subsection{Chapter~\ref{chp:frost}: An Efficient Randomized Threshold Schnorr Signature Scheme}

The first contribution of this dissertation is to define FROST,
a Flexible Round-Optimized Schnorr Threshold Signature scheme.
FROST is a two-round randomized threshold Schnorr signature scheme,
which can optionally be used in the preprocessing setting.
FROST defines a multi-party signing protocol that outputs a signature that is
verifiable under the single-party Schnorr signature verification algorithm~\cite{Schnorr91}.

By saying that FROST can be used in the preprocessing setting,
we mean that FROST can be used in the setting where the first round is performed in a batched manner.
In other words,
performing the threshold signing protocol may require only a single online round of interaction among all parties,
if the first round is performed in a batched manner by each signing party.

While threshold Schnorr signature schemes certainly existed in the literature prior to FROST,
all prior schemes fall into one of two categories.
Prior schemes either require more than two rounds of interaction among all parties~\cite{StinsonR01},
or are insecure in a concurrent setting~\cite{GennaroJKR03}
due to a polynomial-time forgery attack~\cite{DrijversEFKLNS19,BenhamoudaLLOR20}.

One might ask why limiting the number of communication rounds when performing signing is in fact desirable.
What we have learned from practitioners is that round efficiency is highly desirable for implementations in practice,
due to the complexities that arise when coordinating communication rounds among multiple parties.
In the setting where parties could fail to reply or respond in a delayed manner,
managing timeouts and session state across concurrent signing sessions becomes highly complex when signing is performed at scale.

We note that FROST achieves improved round efficiency in the optimistic case that no participant fails to respond or misbehaves.
However, in the case where a participant contributes malformed
values during the protocol or simply fails to respond,
honest parties can identify and exclude the misbehaving participant, and then re-run the protocol.
In other words,
FROST does allow for some form of identifiable abort,
but is not robust,
in that any deviation from the protocol requires aborting and re-running.

We prove the security of FROST with respect to the Algebraic One-More Discrete
Logarithm  (\AOMDL) assumption,
formalized by Nick et al.~\cite{NickRS21}.
which is a weaker variant of the One-More Discrete Logarithm (\OMDL) assumption~\cite{BellareNPS03,BauerFP21}.
While FROST was proven secure with respect to \OMDL~\cite{BellareCKMTZ22},
we additionally show how this proof extends to \AOMDL.
\OMDL defines an interactive discrete-logarithm assumption,
in which the adversary is given $\ell+1$ discrete logarithm challenges,
and is required to output $\ell+1$ solutions,
while being given $\ell$ queries to a discrete-logarithm solution oracle.
\OMDL is a stronger security assumption,
as the \OMDL oracle must output solutions to arbitrary group elements,
and so the oracle is not guaranteed to run in polynomial time.
\AOMDL additionally requires the adversary to give as input the representation of the input group element with respect to all challenge group elements.
As such, the \AOMDL solution oracle is guaranteed to run in polynomial time,
therefore making \AOMDL a weaker assumption than \OMDL.

\subsection{Chapter~\ref{chp:storm}: A Generic Distributed Key Generation (DKG) Construction}

The second contribution of this dissertation is to define a simple generic distributed key generation (DKG) construction.
While key generation for threshold signature schemes can be performed in a centralized manner using a trusted dealer,
often distribution of trust is likewise required during the generation of key material.
As such,
DKG schemes allow participants to collaborate to generate asymmetric key material in such a way that the secret key is unknown and secret shared among all participants.

Our generic DKG construction relies on three cryptographic building blocks:
a secure hash function,
an \emph{Aggregatable Verifiable Secret Sharing} (AgVSS) scheme,
and a \emph{Non-Interactive Key Exchange} (NIKE) scheme.
We show how Feldman's VSS~\cite{Feldman87}  can be augmented to be used as an AgVSS.

The goal for presenting a generic DKG is to enable flexibility for implementations and standardization efforts.
Future implementations may wish to opt for different building blocks,
and so a generic construction allows for different choices while maintaining formal guarantees of security.
Further,
this flexibility may be worthwhile to ongoing NIST standardization efforts for threshold schemes~\cite{NIST23}.
The utility of a generic DKG is that any instantiation of the DKG will remain secure,
so long as each underlying building block is secure.

We give a concrete construction of our generic DKG which we call Storm,
which builds upon Feldman's VSS~\cite{Feldman87}  and a straightforward discrete-logarithm NIKE,
which we define in Section~\ref{concrete-nike}.

\subsection{Chapter~\ref{chp:arctic}: An Efficient Deterministic Threshold Schnorr Signature Scheme}

The third contribution of this dissertation is to define a \emph{deterministic} threshold Schnorr signature scheme.
While FROST is desirable in practice,
one downside is that participants cannot re-use secret state across signing sessions,
as doing so will result in complete exposure of their secret signing key.
In the real-world setting where machines can go offline and reboot without warning,
such a strong requirement can prove challenging in practice.
The goal of a deterministic threshold signature scheme is to protect against such cases,
as participants are no longer required to maintain state when performing signing.

Towards this goal, we present Arctic,
a deterministic and stateless threshold Schnorr signature scheme.
The primary goal of Arctic is simplicity.
While prior deterministic threshold Schnorr signature schemes have been defined~\cite{NickRSW20,GarillotKMN21,KondiOR23} in the literature,
these prior schemes rely on either generic multi-party computation techniques,
or generic non-interactive zero-knowledge proof systems,
and therefore incur complexity and performance overhead.
The observation underlying Arctic is that in settings where the expected number of honest parties outnumbers the number of corrupt parties,
we can define a simpler and more efficient deterministic threshold Schnorr signature scheme.

In particular,
for moderately sized groups (i.e., when $n \leq 20$),
Arctic is more than an order of magnitude more efficient than existing deterministic schemes in the literature~\cite{NickRSW20,GarillotKMN21,KondiOR23}
Arctic is three orders of magnitude more efficient when $n \leq 10$.
For larger groups,
Arctic scales linearly relative to the number of processing cores.
Importantly,
signers in Arctic are required to generate and maintain secret keys,
but otherwise do not need to manage secret state.

We prove the security of Arctic by showing a reduction to the Discrete-Logarithm (DL) problem in the Random Oracle Model (ROM).
Showing a reduction to standard security assumptions in the ROM is highly desirable,
as these assumptions are the same as is required for the security of the single-party Schnorr signature scheme~\cite{Schnorr91}.

\section{Impact in Practice}
\label{intro:impact}

The main impact this thesis has had in practice is the implementation and standardization of FROST,
which we now describe.

The Zcash Foundation has implemented FROST and incorporated FROST into the core Zcash protocol~\cite{ZcashFROSTImpl,ZcashFROSTZip}.
FROST is used to partition a spending key for a Zcash wallet into multiple shares.
As such,
FROST allows a Zcash user to issue a transaction only after a threshold number of signing shares are used to produce a signature.
FROST improves over prior schemes such as Bitcoin's multisig design~\cite{BitcoinMultisig},
in that a FROST signature does not leak the number of signers and hence avoids fingerprinting attacks on-chain.
Bitcoin's multisig design,
on the other hand,
simply concatenates $t$ signatures into one joint signature,
where the public key is the set of $n$ public keys.

FROST has been defined as an informational RFC for the Crypto Forum Research Group (CFRG) within the IRTF~\cite{Connolly22}.
FROST is the first threshold signature scheme to be defined within an IRTF RFC.
The scheme is defined to be agnostic to any particular choice of parameters,
and supports a range of parameter choices.
Furthermore,
the RFC does not define how key generation is performed,
and simply assumes that participants are initialized with secret signing shares that are Shamir secret shares of a signing key.
The RFC therefore is compatible with any key generation RFC that might be defined in the future which outputs keys of this form.

Other blockchains beyond Zcash have investigated the use of FROST to perform multi-party signing,
most notably, Bitcoin.
There is existing effort to define FROST as a Bitcoin Improvement Proposal (BIP)~\cite{FROSTBip} and build additional infrastructure with FROST in mind,
including distributed key generation~\cite{ChillDKG}.
FROST is also used within the context of bridging mechanisms,
allowing funds to flow from Bitcoin to other blockchain networks~\cite{ArchFROST}.
The security of FROST has also been discussed within the Ethereum community~\cite{FROSTEthereum}.

There is additionally a team working to define a FROST submission for the NIST threshold signature scheme call for proposals~\cite{NIST22,NIST23}.
Portions of this dissertation will be employed towards this effort;
namely,
the proof for \AOMDL security of FROST,
which is a weaker assumption than \OMDL,
which prior proofs of security rely upon~\cite{BellareCKMTZ22}.
We hope that the submission of FROST to the NIST call for threshold schemes allows for more widespread adoption of threshold signatures beyond the cryptocurrency space,
into domains such as banking and digital certificate management.
