\subsection{Indistinguishability}
\label{defn:indistinguishability}

The security of any key generation protocol requires that the secret key be hard to guess or learn from the public transcript.
In the single-party setting, the adversary does not have any influence over the sampling of key material,
and so guaranteeing this property is straightforward.
However, because the adversary is an active participant in a distributed key generation protocol,
we must ensure that a subset of at most $t-1$ colluding players cannot bias key material.

To establish this property,
we require that a DKG must generate keys that are \emph{indistinguishable} from keys output by the target key generation algorithm.
This property is implied by the notion of secrecy if the underlying
construction assumes a one-to-one correspondence between secret and public
keys.
For example, the Gennaro et al.\ notion of simulatability assume that indistinguishability of the resulting keypair is an implicit consequence of the ability to simulate with respect to a public key.
However, simulatability does not necessarily imply indistinguishability,
because the zero-knowledge game \emph{only} guarantees the indistinguisahbility of public key material between the real and simulated environments.
If there is a one-to-one relation between public and secret keys,
proving zero-knowledge implies indistinguishability.
For cryptosystems where a one-to-many relation exists between public and private keys,
such as in lattice-based cryptosystems,
proving that a DKG is zero-knowledge does \emph{not} imply indistinguishability from its target key generation scheme.


Because our generic construction similarly assumes a one-to-one correspondence
of secret and public keys, we do not make use of this notion of
indistinguishability in the proof of security for our generic construction, as
the proof of zero-knowledge implies indistinguishability.
Hence, for future reference, we give the notion of indistinguishability more formally in
Appendix~\ref{app:indistinguishability}.

