\section{Future Work and Composability}
\label{storm:future-work}

Because we prove the generic construction secure with respect to our game-based
notions,
we do not inherently prove that the generic construction is secure with respect
to any other protocol;
i.e., we do not prove security under composability.
One approach to demonstrating composability is using the Universal Composability (UC) framework~\cite{Canetti01}.
However, a second approach would be to prove that a DKG that is secure under
these game-based notions is likewise secure under a simulation-based notion.
Such an approach was taken by Boneh et al.~\cite{BonehHL24} to show equivalence between
their game-based notions of security for an Exponent Verifiable Random Function (eVRF),
and a simulation-based notion of security.

To do so, we first must determine which notion of simulation-based security our game-based notions capture.
Katz~\cite{Katz24} gives several notions of simulation-based security for DKGs,
defining full security as a DKG whose output keys are indistinguishable from keys
from the target single-party key generation algorithm.
He defines security with abort as a DKG that achieves full security with the
exception of an adversary that can force honest participants to abort (and
hence introduce bias).

We postulate that it is possible to prove a DKG that is weakly robust,
zero-knowledge, and indistinguishable under the simulation-based notion of
security with aborts.
Note that if the weakly robust DKG additionally implemented identifiable aborts and re-ran the protocol,
it may be possible for the DKG to achieve full security,
as the adversary would be able to terminate the protocol early but not learn sufficient information about the public key before doing so.
Furthermore, we postulate that it is possible to prove a DKG that is strongly
robust, zero-knowledge, and indistinguishable under the simulation-based notion
of full security.
