\section{Related Work}
\label{frost-related-work}

In this section,
we present related work to FROST.
We consider work published prior to FROST,
as well as subsequent work.
Importantly,
all prior related Schnorr threshold signatures are either vulnerable to a forgery attack against a concurrent adversary~\cite{DrijversEFKLNS19},
or do not allow for single-round online signing.

\subsection{Prior Related Work}

We now review prior threshold schemes with a focus on Schnorr-based designs,
and split our review into robust and non-robust schemes. Robust schemes ensure that
so long as $t$ participants correctly follow the protocol, the protocol is
guaranteed to complete successfully, even if a subset of
participants (at most $n-t$) contribute malformed shares.
Conversely, designs that are not robust simply abort after detecting any
participant misbehaviour.

\textbf{Robust Threshold Schemes.} Stinson and Strobl~\cite{StinsonR01}
present a threshold signature scheme
producing Schnorr signatures, using the modification of Pedersen's DKG presented
by Gennaro et al.~\cite{GennaroJKR07} to generate
both the secret key $s$ during key generation as well as
the random nonce $k$ for each signing operation.
This construction
requires at minimum four rounds
for each signing operation (assuming no participant misbehaves): three rounds
to perform the DKG to obtain $k$,
and one
round to distribute signature shares and compute the group signature.
Each round requires participants to send values to every other participant.

Gennaro et al.~\cite{GennaroJK02} present a threshold
Schnorr signature protocol that uses Pedersen's
DKG~\cite{Pedersen91} to generate both $s$ during key generation
and the random nonce $k$ for signing operations.
However, this scheme is insecure against ROS attacks~\cite{DrijversEFKLNS19}.
Pedersen's DKG requires two rounds among participants,
and so this construction requires an additional round for signing.
Each round requires that
all participants send values to all other participants.
The authors also discuss an optimization that leverages
a \emph{signature aggregator} role, an entity trusted to
gather signatures from each participant, perform validation, and publish the
resulting signature, a role we also adopt in our work.
In their optimized variant, participants can perform
Pedersen's DKG to generate multiple $k$ values in a pre-processing stage independently
of performing signing operations.
In this variant, to compute $\ell$ signatures, signers first perform two
rounds of $\ell$ parallel executions of Pedersen's DKG,
thereby generating $\ell$
random nonces. The signers can then store these pre-processed values to later perform
$\ell$ single-round signing operations.

Importantly, the signing operation defined by FROST \emph{does not} perform a DKG
during signing operations as is done in both of the above schemes~\cite{StinsonR01,GennaroJK02},
but instead make use of additive secret sharing and share conversion.
Consequently, FROST trades off robustness for more efficient signing
operations,
such that a misbehaving participant can cause the signing operation to abort.
However, such a tradeoff is practical to many real-world settings.


\textbf{Non-Robust Threshold Schemes.} FROST is not unique in trading off
favouring increased network efficiency over robustness.
Gennaro and Goldfeder~\cite{GennaroG19} present a threshold ECDSA
scheme that similarly requires aborting the protocol in the case of
participant misbehaviour. Their signing construction uses a two-round DKG to generate
the nonce required for the ECDSA signature, leveraging additive-to-multiplicative share
conversion. This DKG has been also applied in a Schnorr threshold
scheme context to generate the random nonce for more efficient distributed key
generation operations~\cite{kzen-schnorr} in combination with threshold Schnorr
signing operations~\cite{StinsonR01}.
In later work~\cite{GennaroG20}, Gennaro and Goldfeder define an optimization
to a single-round ECDSA signing operation with a
preprocessing stage, which assumes the protocol will abort in the case of
failure or participant misbehaviour.
Their end-to-end protocol with identifiable aborts has eight network rounds,
six of which require broadcasting to all other signing participants,
and two of which require performing pairwise multiplicative-to-additive
share conversion protocols. Further, while the protocol can be optimized into a
preprocessing phase, the choice of the signing coalition must be determined at
the time of preprocessing.
FROST defines a more efficient preprocessing
phase as secret nonces can be generated in a distributed manner in the
preprocessing phase entirely
non-interactively. Further,
participants can ``mix'' preprocessed values across different signing
coalitions, as FROST requires that the choice for the signing coalition be made
only during the second and final round of signing.

Recent work by Damg\aa{}rd et al.~\cite{fast-threshold-ecdsa} defines an efficient
threshold ECDSA construction that similarly to FROST requires aborting in the case of misbehaviour.
%Their design relies on generating a blinding factor
%$d + m \cdot e$ where
%where $d$ and $e$ are $2t$ secret sharings of zero, such
%that the entire binding factor evaluates to zero when all signing parties
%are honest and agree on $m$.
%Their approach is similar to FROST in that signature
%shares are bound to the message and to the set of signing parties.
However, the security of their
scheme requires the majority of participants to be honest, and $n \geq 2t+1$.
Further, their scheme requires all $n$ participants take part in signing
operations, where the threshold $t$ is simply a security parameter.

Similarly to FROST,
Abidin, Aly, and Mustafa~\cite{AbidinAM20} present a design for
authentication between devices,
and use additive secret sharing to generate the nonce for Schnorr
signatures in a threshold setting, a technique
also used by FROST.
However, the authors do not consider the
Drijvers attack~\cite{DrijversEFKLNS19} and consequently their design is similarly limited to restricted levels of parallelism;
i.e., it is not secure against a concurrent adversary.
Further, their design does
not include validity checks for responses submitted by participants when
generating signatures and consequently does not detect nor identify
misbehaving participants.

FROST improves upon prior work in Schnorr threshold schemes by
providing a single-round signing variant with a preprocessing stage that is
agnostic to the choice of the signing coalition. Further, the number of signing
participants in FROST is required to be simply some $t\leq n$,
while remaining secure against the
Drijvers attack~\cite{DrijversEFKLNS19} and other ROS~\cite{schnorr06} attacks.









\subsection{Subsequent Work}

Since the publication of FROST,
the insecurity of the ROS problem has been underscored~\cite{BenhamoudaLLOR20},
and additional concurrently secure threshold Schnorr signature schemes have been proposed.
We now review subsequent works.

\paragraph{Efficient Algorithms for Solving ROS Problems.}
Benhamouda et al.~\cite{BenhamoudaLLOR20} give a polynomial-time algorithm for
solving the ROS (Random inhomogeneities in a Overdetermined Solvable system of linear equation) problem,
which was first introduced by Schnorr~\cite{schnorr06}.
We discuss the ROS problem more in Section~\ref{background:ros}.
Benhamouda et al. then show how the ROS problem can be applied to blind and threshold Schnorr signatures,
to produce a forgery in polynomial time.

\paragraph{Concurrently Secure Threshold Schnorr Signatures.}
FROST2~\cite{BellareCKMTZ22} is an optimized version of FROST that reduces the number of exponentiations required for signing from $\thresh$ to one.
A further optimization of FROST2, called FROST3, is introduced by Ruffing et al.~\cite{RuffingRJSS22},
and proven secure with a DKG by Chu et al.~\cite{ChuGRS23}.
All three of FROST, FROST2, FROST3 are proven statically secure under the algebraic one-more discrete logarithm assumption (AOMDL)~\cite{BellareCKMTZ22}.

Lindell presents a three-round threshold Schnorr signature~\cite{Lindell22} with the goal of
defining a scheme that is both secure against ROS attacks and
secure in the random oracle model under the discrete logarithm assumption only.
Static security is modeled in the universal composability framework (UC)~\cite{Canetti01} and therefore captures a concurrent adversary.

Sparkle~\cite{CritesKM23} is a three-round threshold Schnorr signature scheme
that is proven secure under $\tcor$ adaptive corruptions.
In order to achieve full adaptive security,
the authors rely on the algebraic one-more discrete logarithm assumption (AOMDL) in the AGM and ROM.
When the adversary is limited to making $\tcor/2$ corruptions, however,
the authors prove the adaptive security of Sparkle under only AOMDL in the ROM,
by a reduction that rewinds.

Makriyannis~\cite{Makriyannis22} defines a commit-reveal threshold
Schnorr signature scheme similar to Sparkle,
called Classic S., and proves security with
respect to an idealized notion of threshold signatures by Canetti et al.~\cite{CanettiGGMP21}.
They consider adaptive security but employ the guessing argument that incurs exponential tightness loss relative to the number of parties.



